### 2022-01-08 Manuscript/Manuscript_Eli.Rmd
update manuscript

<div class = "space" id = "tab4">
<p class = "caption">Table 4. <em>Predictive performance of algorithms</em></p>
```{r resmetrics, echo=F}
results <- readRDS("../Results/Results.RData")

datatable(round(results$performance,2), options = list(dom = 't'))
```
</div>

@@

<div id = "AppendixA" class = "space">
Appendix A
==================
<br>
```{r exercise, echo=FALSE}
#![Image 1: *Graphic Representation of Thesis*](../Images/Exercise.png)
knitr::include_graphics("../Images/Exercise.png")
knitr::include_graphics("../Images/Exercise2.png")

```
</div>
<br><br>

>>>>

<div class = "space" id = "tab4">
<p class = "caption">Table 4. <em>Predictive performance of algorithms</em></p>
```{r resmetrics, echo=F}
results <- readRDS("../Results/Results.RData")
datatable(round(results$performance,2), options = list(dom = 't'))
```
</div>

@@

<div id = "AppendixA" class = "space">
Appendix A
==================
<br>
```{r exercise, echo=FALSE}
#![Image 1: *Graphic Representation of Thesis*](../Images/Exercise.png)
knitr::include_graphics("../Images/Exercise.png")
knitr::include_graphics("../Images/Exercise2.png")
```
</div>
<br><br>

### 2022-01-08 Script/1 Preprocessing_and_feature_calc.Rmd
update manuscript

###export to CSV so python can do the other calculations
```{r}
write.csv(textdocs, '../Data/3 Data_Processed.csv')
write.csv(passage, '../Data/4 Passage_Processed.csv')

##python
used Python libraries
```{python}
import pandas as pd
import numpy as np
import re
from rouge_score import rouge_scorer as rs #rouge algorithm 
from nltk import ngrams
```
load in data and pre-process passage
```{python}
textdocs = pd.read_csv('../Data/3 Data_Processed.csv', encoding = 'latin-1') #reading in preprocessed data

@@

passage[0:3] #it contains some characters that are not letters at the start and end due to the fact it was once an array
passage[-3:]

>>>>

###export to CSV so python can do the other calculations
```{r}
write.csv(textdocs, '../Data/3 Data_Processed.csv')
write.csv(passage, '../Data/4 Passage_Processed.csv')
```

##python
used Python modules
```{python}
import pandas as pd
import numpy as np
from rouge_score import rouge_scorer as rs #rouge algorithm

```
load in data and pre-process passage
```{python}
textdocs = pd.read_csv('../Data/3 Data_Processed.csv', encoding = 'latin-1') #reading in preprocessed data

@@

#passage[0:3] #it contains some characters that are not letters at the start and end due to the fact it was once an array
#passage[-3:]

### 2022-01-08 Script/2 Analyses.Rmd
update manuscript

###Ridge
```{r}
K <- 10 #number of CVs

set.seed(6164900)
Ridgecv <- cv.glmnet(x = train[, 2:ncol(train)], y = train[,1], alpha = 0, family = 'gaussian', standardize = F,
                    nfolds = K) #setting alpha to 0, runs Ridge.

>>>>

###Ridge
```{r}
set.seed(6164900)
Ridgecv <- cv.glmnet(x = train[, 2:ncol(train)], y = train[,1], alpha = 0, family = 'gaussian', standardize = F,
                    nfolds = K) #setting alpha to 0, runs Ridge.
